Application of Network Flow and Linear Programming to Scheduling of Clinicians

### 2019-07-29 paper/paper.results.tex
Add table for 2017 and comparison table

\subsection{Infectious Diseases Division}
We used clinician time-off requests and minimum/maximum requirements from 2015-2018 as input data for the LP problem. Tables \ref{tbl:2018-schedule-comparison}, \ref{??}, \ref{??} present the optimal schedule generated using the software as well as the manually created schedule, color-coded to distinguish between the different clinicians assigned.

\include{tbl/2018_schedule_comparison}

In order to evaluate the generated schedule and compare it with the manually created schedule, we outline the adherence of each schedule to the constraints presented in section \ref{???}. As we can see, the generated schedule was able to satisfy all mandatory constraints, however for the years of [???] it could not find an optimal schedule while ensuring that the block assignments are spread out ([???] constraint). On the other hand, we can see that the manually created schedule was not able to satisfy all mandatory constraints. In particular, we see that it contains consecutive block assignments for the years of [???], [...]. Evaluating the objectives, we see that [...\textit{request conflicts}]. Moreover, the manual schedule does not attempt to align weekend assignments with block assignments, unlike the optimal schedule found by the software.

>>>>

\subsection{Infectious Diseases Division}
We used clinician time-off requests and minimum/maximum requirements from 2015-2018 as input data for the LP problem. Tables \ref{tbl:2017-schedule-comparison}, \ref{tbl:2018-schedule-comparison}, \ref{??}, \ref{??} present the optimal schedule generated using the software as well as the manually created schedule, color-coded to distinguish between the different clinicians assigned.

\include{tbl/2017_schedule_comparison}
\include{tbl/2018_schedule_comparison}

In order to evaluate the generated schedule and compare it with the manually created schedule, we outline the adherence of each schedule to the constraints presented in section \ref{???}. As we can see from table \ref{tbl:constraints-comparison}, the generated schedule was able to satisfy all mandatory constraints, however for the years of [???] it could not find an optimal schedule while ensuring that the block assignments are spread out ([???] constraint). On the other hand, we can see that the manually created schedule was not able to satisfy all mandatory constraints. In particular, we see that it contains consecutive block assignments for the years of [???], [...]. Evaluating the objectives, we see that [...\textit{request conflicts}]. Moreover, the manual schedule does not attempt to align weekend assignments with block assignments, unlike the optimal schedule found by the software.

\include{tbl/constraints_comparison}
